Predicting Tags for StackOverflow Posts

### 2013-06-27 stackExchange/writeups/iccm-2013/writeup.tex
Final revision
Former-commit-id: 3791c8f9eaa95dc92cb83845716a7056d2c13830 [formerly 2c3cdc4133127b114d44681635b91c19df964e3b]
Former-commit-id: 7cc9c5b3d5cb527dbb20d44040ae427c67ca8aaf

Base-level activation ($B_{i}$) is the log prior odds of observing tag $i$ in the world.
The log prior odds are based on both frequency and recency of use.
However, we are assuming that frequency of tag use does not change greatly between Jul' 08 and Apr' 11 (time period of dataset).
This is a reasonable assumption for the StackOverflow dataset, since tags relate to programming languages, and the rank of programming-language popularity has not changed drastically within the past few years.
This also makes calculating the priors computationally tractable for this large-scale dataset, because the prior log odds can be computed based on frequency only, as is indicated in Table \ref{sample-table}.
So the tag with the highest frequency (\emph{C\#}) would have the highest base-level activation.

>>>>

Base-level activation ($B_{i}$) is the prior log odds of an author using tag $i$.
The prior log odds are based on both frequency and recency of use.
However, we are assuming that frequency of tag use does not change greatly between Jul' 08 and Apr' 11 (time period of dataset).
This is a reasonable assumption for the StackOverflow dataset, since tags relate to programming languages, and the rank of programming-language popularity has not changed drastically within the past few years.
This also makes calculating the priors computationally tractable for this large-scale dataset, because the prior log odds can be computed based on frequency only, as is indicated in Table \ref{sample-table}.
So the tag with the highest frequency (\emph{C\#}) would have the highest base-level activation.
